Is it time for an NBA expansion?

### 2024-04-12 paper/paper.qmd
Made Some Graphs

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

>>>>

@@

# Reshape data from wide to long format
nba_data_long <- nba_data %>%
  pivot_longer(cols = c(AST, TRB, PTS, STL, BLK), names_to = "Statistic", values_to = "Value")

line_colors <- c("red", "green", "blue", "purple", "orange")

exp_year <- c(1988, 1989, 1995, 2004)

combined_plot <- ggplot(nba_data_long, aes(x = Year, y = Value)) +
  geom_point(color = "black") +  # All points in black
  geom_smooth(method = "lm", aes(color = Statistic), se = FALSE) +  # Lines of best fit with different colors
  scale_color_manual(values = line_colors) +
  geom_vline(xintercept = exp_year, color = "black", linetype = "dashed") +
  facet_wrap(~Statistic, scales = "free_y") +  # Facet by statistic, with free y scales
  labs(title = "NBA Stats Over Years", x = "Year", y = "Value") +
  theme_minimal() +
  theme(legend.position = "none")

combined_plot
